### 2019-03-04 IEEE_TC_submission.d/symmetry_properties.tex
ssr

\hspace*{1in}
$x_i : a_i ~\longrightarrow~ b_i$.

@@

\noindent
Examples of properly $n$-symmetric $n$-variable NCFs satisfying the
conditions of Theorem \ref{thm:ncf_r_symmetric} are the following.
For each $n > 1$, let $f_n$ be the function defined by the following
formula:

@@

@@

\noindent
\hspace*{0.5in}
$x_1:~ 1 ~\longrightarrow~ 1$ \\
\hspace*{0.5in}
$x_2:~ 1 ~\longrightarrow~ 0$ \\
\hspace*{0.5in}
$x_3:~ 1 ~\longrightarrow~ 1$ \\
\hspace*{0.75in}
$\vdots$

@@

\noindent
\hspace*{0.5in}
$x_n:~ 1 ~\longrightarrow~ 1$

@@

\noindent
\hspace*{0.5in}
$x_n:~ 1 ~\longrightarrow~ 0$.

>>>>

\hspace*{0.25in}
$x_i : a_i ~\longrightarrow~ b_i$.

@@

\noindent
We now provide
examples of properly $n$-symmetric $n$-variable NCFs satisfying the
conditions of Theorem \ref{thm:ncf_r_symmetric}.
For each $n > 1$, let $f_n$ be the function of $n$ variables, namely
$x_1, \ldots, x_n$, defined by the following formula:

@@

\noindent
\hspace*{0.25in}
$x_1:~ 1 ~\longrightarrow~ 1$ \\
\hspace*{0.25in}
$x_2:~ 1 ~\longrightarrow~ 0$ \\
\hspace*{0.25in}
$x_3:~ 1 ~\longrightarrow~ 1$ \\
\hspace*{0.75in}
$\vdots$

@@

@@

\noindent
\hspace*{0.25in}
$x_n:~ 1 ~\longrightarrow~ 1$

@@

\noindent
\hspace*{0.25in}
$x_n:~ 1 ~\longrightarrow~ 0$.
